\documentclass{homework}
\course{Math 6802}
\author{Jim Fowler}
\input{preamble}

\newcommand{\Q}{\mathbb{Q}}

\begin{document}
\maketitle

\begin{inspiration} Without fantasy one would never become a
mathematician, and what gave me a place among the mathematicians was
the audacity of my thinking. \byline{Sophus Lie}
\end{inspiration}

\section{Terminology}

\begin{problem} For a cycle $\sigma \in H_k(X)$ and a cocycle $\varphi \in H^\ell(X)$, define the cap product $\sigma \smallfrown \varphi$.
\end{problem}

\begin{problem} For oriented closed $n$-manifolds $M$ and $N$, what is
the \textbf{degree} of a map $f : M \to N$?
\end{problem}

\section{Numericals}

\begin{problem} Let $\Sigma_2$ be the orientable genus two surface,
and $[\Sigma_2] \in H_2(\Sigma_2)$ a fundamental class. Compute the
map $[\Sigma_2] \smallfrown - : H^1(\Sigma_2) \to H_1(\Sigma_2)$ and
verify that is an isomorphism.
\end{problem}

\section{Exploration}

\begin{problem} Compute $H^\star(\CP^n)$ as a ring.  \textit{Hint:}
invoke Poincar\'e duality to make this much easier than the direct
computation we sketched in lecture.
\end{problem}

\begin{problem} An oriented closed connected manifold is
\textbf{flexible} if it admits a self-map that has degree not zero or
$\pm 1$.  Show that $S^k$ and $\CP^k$ and any products of such are
flexible.
\end{problem}

\begin{problem}
  For a connected closed orientable $4k$-manifold $M$, explain why the cup product map
  \[
    \smallsmile : H^{2k}(M;\Q) \otimes 
    H^{2k}(M;\Q) \to H^{4k}(M;\Q) \cong \Q
  \]
  is a nondegenerate symmetric bilinear form.

  Define the signature $\sigma(M)$ to be the signature of the cup
product pairing on cohomology in the middle dimension.
\end{problem}

\section{Prove or Disprove and Salvage if Possible (PODASIP)}

\begin{problem} % missing compactness assumption
  The Euler characteristic of an odd-dimensional manifold vanishes.
\end{problem}

\begin{problem}
  For an integer $n \in \Z$, there exists a connected closed oriented 4-manifold $M$ with $\chi(M) = n$.
\end{problem}

\begin{problem}
  For an integer $n \in \Z$, there exists a connected closed oriented 4-manifold $M$ with $\sigma(M) = n$.
\end{problem}

\end{document}
