\documentclass{homework}
\course{Math 6802}
\author{Jim Fowler}
\input{preamble}

\begin{document}
\maketitle

\begin{inspiration}
  With our mid-course correction, this is our the final exam --- and it is due May 3 at noon.
  \byline{Jim Fowler}
\end{inspiration}

\section{Terminology}

\begin{problem}
  What is a Hopf algebra?  (You have some choices here!)
\end{problem}

\begin{problem}
 What is a homology sphere? 
\end{problem}

\section{Numericals}

\begin{problem}
  Compute $H_n(\CP^n \times \CP^m; \Z)$.
\end{problem}

\begin{problem}
  For a compact contractible manifold $M^n$, compute $H_n(\partial M)$.
\end{problem}

\section{Exploration}

% \begin{problem} Let $M$ be a closed $n$-manifold which is a
% homology sphere, and define $\ddot{M}$ to be $M$ with two points
% removed.

%   Compute
%   $H_\star(\ddot{M})$,
%   $H^\star(\ddot{M})$, and
%   $H_c^\star(\ddot{M})$.
% \end{problem}

\begin{problem}
  Sometimes manifolds have finite covers which are homeomorphic to the
  original manifolds, e.g., $S^1$ or the $n$-torus.

  Is it possible that a closed manifold $M^n$ has an infinite-sheeted
  cover which is homotopy equivalent to itself?
\end{problem}

\begin{problem}
  Let $\Sigma_2$ be the closed surface of genus~$2$; find a map $f :
  \Sigma_2 \to \Sigma_2$ which is not homotopic to the identity, but
  for which $f^\star : H^\star(\Sigma_2) \to H^\star(\Sigma_2)$ is the
  identity.  This is an element of the \textbf{Torelli group}.
\end{problem}

\section{Prove or Disprove and Salvage if Possible (PODASIP)}

\begin{problem}
  A manifold does not retract onto its boundary.
\end{problem}

\begin{problem}
  For a finite CW complex $X$, write
  $H^{\mbox{\scriptsize free}}_n(X)$ and 
  $H^{\mbox{\scriptsize tors}}_n(X)$ for the free and torsion pieces of $H_n(X)$, respectively.
  Then $H^n(X) \cong  
  H^{\mbox{\scriptsize free}}_n(X) \oplus
  H^{\mbox{\scriptsize tors}}_n(X)$.
\end{problem}

\begin{problem}
  For a space $X$, the first cohomology group $H^1(X)$ is torsion-free.
  \end{problem}


\end{document}
